Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-04 PAPER.tex
changed caption for bootstrapping plot

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping 
methods. The data is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the 
effects of bootstrapping from signal loss. Three different bootstrapping methods are shown: the blue and black use methods 
where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly 
sampled. It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent 
samples (only the last baseline spot is sampled randomly), as shown by the black curve. In red, bootstrapping occurs over both 
the baseline and time axes, illustrating how errors can be under-estimated if sampling more values than independent ones 
(fringe-rate filtering reduces the number of independent samples). We use the method illustrated by the black curve in our 
updated analysis, which is shown to agree with the $2\sigma$ analytic prediction for noise (green).}
	\label{fig:data_errors}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and two different bootstrapping 
methods. The data is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the 
effects of bootstrapping from signal loss. The bootstrapping method used in A15 in shown in gray, where bootstrapping occurs along both the baseline and time axes. This under-estimates errors by sampling more values than independent ones in the dataset (fringe-rate filtering reduces the number of independent samples along time). We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis. This is shown to agree with the $2\sigma$ analytic prediction for noise (green).}
	\label{fig:data_errors}
\end{figure}
